---
title: 'Homework #4'
author: "Zhejin Dong(zd2221)"
date: "11/14/2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
Anually_data<-read.csv('/Users/zhejindong/Downloads/__public__data__castnet__download__Castnet_4B31B9F8659F5BF4F2868247415B43B4_11_14_2018_093807/Concentration - Annual.csv')
Season_data<-read.csv("/Users/zhejindong/Downloads/__public__data__castnet__download__Castnet_4B31B9F8659F5BF4F2868247415B43B4_11_14_2018_093807/Concentration - Seasonal.csv")
Week_data<-read.csv("/Users/zhejindong/Downloads/__public__data__castnet__download__Castnet_4B31B9F8659F5BF4F2868247415B43B4_11_14_2018_093807/Concentration - Weekly.csv")
```


```{r}
library(tidyverse)
Anually_data$YEAR<-as.character(Anually_data$YEAR)
Anually_data$YEAR<-paste0(Anually_data$YEAR,"-01-01")
Anually_data$YEAR<-as.Date(Anually_data$YEAR)
data1<-filter(Anually_data,YEAR>='2008-01-01')
data1$SITE_ID<-factor(data1$SITE_ID,levels=c('CTH110','CAT175','NIC001','WFM105','HWF187','WFM007'),
                      labels=c('Connecticut Hill','Claryville','Nicks Lake','Whiteface Mountain','Huntington Wildlife Forest','NULL'))
```


```{r}
ggplot(data1,aes(x=YEAR,y=data1$SO4_CONC,group=data1$SITE_ID,color=SITE_ID)
       )+geom_line()+scale_x_date(date_labels = "%Y",date_breaks = '1 year'
                                  )+geom_point()+ggtitle('Decreasing SO4 by Years')+ylab('SO4')
```


The picture above shows that SO4 content in 5 districts in NYC decreases by years from 2009 to 2017. 


```{r}
Week_data$DATE<-substr(Week_data$DATEON, 1, 10)
Week_data$DATE<-as.Date(Week_data$DATE,'%m/%d/%Y')
Week_data$Month<-substr(Week_data$DATE,6,7)
Week_data$YEAR<-factor(Week_data$YEAR)
```
```{r fig.width==10}
data2<-select(Week_data,Month,YEAR,SO4_CONC)
data2<-filter(data2,SO4_CONC!='NA')

data3<-data2 %>% group_by(Month,YEAR) %>% summarise_at(vars(SO4_CONC),mean)

ggplot(data3,aes(x=Month,y=SO4_CONC,group=1))+geom_line()+facet_grid(~YEAR)+ggtitle('SO4 Content Month Fluctuation')+ylab('SO4 Content')
```

From the picture above, we can found two changes from 2008 to 2018:

1 The total annually SO4 content is decreasing.

2 The variance of SO4 in a year is decreasing.



```{r}
data7<-filter(data2,YEAR %in% c('2008','2012','2017'))
data6<-data7 %>% group_by(Month,YEAR) %>% summarise_at(vars(SO4_CONC),mean)
ggplot(data6, aes(Month,SO4_CONC)) + geom_col(fill='darkred')+ xlab("SO4")+facet_wrap(YEAR~.)+xlab('Month')+ggtitle('SO4 Content Month Fluctuation in Three Typical Years')
```


I selected three typical years to display in detail the fluctuation of SO4 in 12 months. I found, before 2012, SO4 content is quite high in from June to July, but this situation weakens by years. 

